---
title: "Tutorial 5 EDA"
author: "Nur Aliah Hasshim"
date: "4/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exploring Data with R


### 1. See basic descriptive statistics
```{r}
summary(attitude)
```

#### a) The differences between (attitude[3]) and attitude$learning)
```{r}
attitude[3] #returns third column values in matrix form
attitude$learning #returns "learning" column values in list form
```

### 2. List of variables in the dataset
```{r}
colnames(attitude)
```

### 3. Number of rows in a dataset
```{r}
nrow(attitude)
```

### 4. Number of columns in dataset

```{r}
ncol(attitude)
```

### 5. Structure of dataset
```{r}
str(attitude)
```

### 6. First 6 rows of dataset by default
```{r}
head(attitude)
```
### 7. First 15 rows of dataset
```{r}
head(attitude,15)
```
### 8. All rows of dataset but the last row
```{r}
head(attitude,-1)
```
### 9. Last 6 rows of dataset by default
```{r}
tail(attitude)
```
### 10. Last 12 rows of dataset
```{r}
tail(attitude, 12)
```
### 11. All rows of dataset but the first row
```{r}
tail(attitude,-1)
```
### 12. Number of missing values
```{r}
sum(is.na(attitude))
```
### 13. Number of missing values in "Learning" variables
```{r}
sum(is.na(attitude$learning))
```
### 14. Simple graph on a screen device
```{r}
hist(attitude$learning, col = "blue")
```

### 15. Graph on a file device (Pdf file)

```{r}
pdf(file="myplot.pdf")
with(attitude, plot(privileges, learning))
abline(h = 12, lwd = 2, lty = 2)
title(main = "Learning Attitude")
dev.off()
```